Towards planning of infantile cardiac surgery based on simulation

### 2012-02-28 Doc/Miccai/shell-model.tex
small comments on section 2
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@343 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

\begin{equation}
  \myvec{f} = K(\myvec{x} - \myvec{x_0})
\end{equation}

For more thorough description we refer the reader to the textbook about
Finite Element methods for example \cite{Reddy1993}.

@@

\begin{figure}[tbh]
  \centering
  \begin{tabular}{cccc}
    \includegraphics[width=0.24\columnwidth]{img/twist-06-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-08-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-16-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-31-cg.png}
  \end{tabular}
  \caption{Convergence on a twisted cylinder with 6, 8, 16 and 31 nodes
  around the circumference (120, 208, 832 and 3038 elements)}
  \label{fig-convergence}
\end{figure}

>>>>

\begin{equation}
  \myvec{f} = K(\myvec{x} - \myvec{x_0})
 \label{linear_static_model} 
\end{equation}

\christian{I think that we should precise that we rely on corotational shell formulation: the model is linear in the local frame of the element, otherwise equation (\ref{linear_static_model}) is false } 
For more thorough description we refer the reader to the textbook about
Finite Element methods for example \cite{Reddy1993}.

@@

\begin{figure}[tbh]
  \centering
  \begin{tabular}{cccc}
    \includegraphics[width=0.24\columnwidth]{img/twist-06-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-08-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-16-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-31-cg.png}
  \end{tabular}
  \caption{Convergence on a twisted cylinder with 6, 8, 16 and 31 nodes
  around the circumference (120, 208, 832 and 3038 elements).
  \christian{Could we add wire-frame images to show the density of the meshes} } 
  \label{fig-convergence}
\end{figure}
